---
title: "R Notebook"
editor_options: 
  chunk_output_type: console
---

## load libs

```{r}
needs(tidyverse, jsonlite)
#library(tidyverse)
options(scipen=999)

```


## load example history

```{r}
matchId = '1001540028'

history = read_json(str_c('scrape/riot/raw/matchhistory/', matchId, '.json'))

names(history)
history$gameCreation
```

## read all match histories
```{r}
path <- "scrape/riot/raw/matchhistory/"
files <- dir(path, pattern = "*.json")

allhistory <- files %>%
  map_df(~fromJSON(file.path(path, .), flatten = TRUE))
```

```{r}
temp <- list.files(path, pattern="*.json", full.names=TRUE)
movies <- purrr::map_df(temp, function(x) { 
  purrr::map(jsonlite::fromJSON(x), function(y) ifelse(is.null(y), NA, y)) 
})
games = movies
```

## number of games over time

```{r}
games %>% 
  ggplot(aes(gameCreation)) + geom_area(stat = "bin", bins=200) 

games %>% 
  ggplot(aes(gameCreation)) + geom_histogram(stat = "bin", bins=200)

games %>% 
  ggplot(aes(seasonId)) + geom_histogram(stat = "bin", bins=100)

games %>% 
  ggplot(aes(gameDuration)) + geom_histogram(stat = "bin", bins=100)

games %>% 
  ggplot(aes(gameDuration)) +
  geom_histogram(stat = "bin", bins=100) +
  facet_wrap(~seasonId)
  

games %>% 
  filter(seasonId == 11) %>% 
  ggplot(aes(gameDuration)) +
  geom_histogram(stat = "bin", bins=100) +
  facet_wrap(~gameVersion)



games %>% 
  filter(seasonId == 11) %>% 
  ggplot(aes(gameDuration)) +
  geom_density(kernel = "gaussian") +
  facet_wrap(~gameVersion)

games %>% 
  filter(seasonId == 11) %>% 
  ggplot(aes(gameVersion, gameDuration)) +
  geom_violin(kernel = "gaussian")

games = games %>% 
  arrange(gameCreation) %>% 
  mutate(
    season = factor(seasonId),
    patch = patchF(gameVersion)
  )

patchF = factor(games$gameVersion)
games$patch = factor(games$gameVersion, levels = unique(games$gameVersion))

games %>% 
  ggplot(aes(patch, gameDuration, color = season)) +
  geom_boxplot() + 
  scale_color_brewer(palette = "Set2") +
  coord_flip()


games %>% 
  ggplot(aes(patch, gameDuration, color = season)) +
  geom_violin() + 
  scale_color_brewer(palette = "Set2") +
  coord_flip()

needs(ggridges)

ggplot(iris, aes(x = Sepal.Length, y = Species)) + geom_density_ridges()

games %>% 
  ggplot(aes(y = patch, x = gameDuration, fill = season)) +
  geom_density_ridges() + 
  scale_color_brewer(palette = "Set2") + 
  xlim(c(1000, 4000))
  #coord_flip()

```

connected scatter plot showing average duration and chance of comeback for each patch


```
needs(parallel, rjson)
json_files<-list.files(path="scrape/riot/raw/matchhistory",pattern="*.json",full.names = TRUE)
cl <- makeCluster(detectCores() - 1)
json_list<-parLapply(cl,json_files,function(x) rjson::fromJSON(file=x,method = "R"))
stopCluster(cl)

```


## chart gold difference and victory time



## line charts of all cs per minute


## chance of winning a losing game


## number of champs picked each patch


## time since champ was picked
 xin hasn't been picked in NA for since 2015


## how far behind the meta is NA


















