---
title: "R Notebook"
editor_options: 
  chunk_output_type: console
---

## load libs

```{r}
needs(tidyverse, jsonlite)
options(scipen=999)

```


## load example history

```{r}
matchId = '1001540028'

history = read_json(str_c('scrape/riot/raw/matchhistory/', matchId, '.json'))

names(history)
history$gameCreation
```

## read all match histories
```{r}
path <- "scrape/riot/raw/matchhistory/"
files <- dir(path, pattern = "*.json")

allhistory <- files %>%
  map_df(~fromJSON(file.path(path, .), flatten = TRUE))
```

```{r}
games = list.files( "scrape/riot/raw/matchhistory/", full.names=TRUE) %>% 
  map_df(function(x) { 
  purrr::map(jsonlite::fromJSON(x), function(y) ifelse(is.null(y), NA, y)) 
  })

games = games %>% 
  arrange(gameCreation) %>% 
  mutate(
    season = factor(seasonId),
    patch = patchF(gameVersion)
  )

games$patch = factor(games$gameVersion, levels = unique(games$gameVersion))
```


## number of games over time

```{r}
games %>% 
  ggplot(aes(gameCreation)) + geom_area(stat = "bin", bins=200) 

games %>% 
  ggplot(aes(gameCreation)) + geom_histogram(stat = "bin", bins=200)

games %>% 
  ggplot(aes(seasonId)) + geom_histogram(stat = "bin", bins=100)

games %>% 
  ggplot(aes(gameDuration)) + geom_histogram(stat = "bin", bins=100)

games %>% 
  ggplot(aes(gameDuration)) +
  geom_histogram(stat = "bin", bins=100) +
  facet_wrap(~seasonId)
  

games %>% 
  filter(seasonId == 11) %>% 
  ggplot(aes(gameDuration)) +
  geom_histogram(stat = "bin", bins=100) +
  facet_wrap(~gameVersion)



games %>% 
  filter(seasonId == 11) %>% 
  ggplot(aes(gameDuration)) +
  geom_density(kernel = "gaussian") +
  facet_wrap(~gameVersion)

games %>% 
  filter(seasonId == 11) %>% 
  ggplot(aes(gameVersion, gameDuration)) +
  geom_violin(kernel = "gaussian")


games %>% 
  ggplot(aes(patch, gameDuration, color = season)) +
  geom_boxplot() + 
  scale_color_brewer(palette = "Set2") +
  coord_flip()


games %>% 
  ggplot(aes(patch, gameDuration, color = season)) +
  geom_violin() + 
  scale_color_brewer(palette = "Set2") +
  coord_flip()

needs(ggridges)

ggplot(iris, aes(x = Sepal.Length, y = Species)) + geom_density_ridges()

games %>% 
  ggplot(aes(y = patch, x = gameDuration, fill = season)) +
  geom_density_ridges() + 
  scale_color_brewer(palette = "Set2") + 
  xlim(c(1000, 4000))
  #coord_flip()

needs("ggthemes")

```


## connected scatter plot showing average duration and chance of comeback for each patch

```{r}
timelines = list.files( "scrape/riot/raw/matchtimeline/", full.names=TRUE) %>% 
  map_df(function(x) { 
    purrr::map(jsonlite::fromJSON(x), function(y) ifelse(is.null(y), NA, y)) 
  })

timelineFrames = timelines$frames

tl1mapped = timelines[[1]]
```


What's in a timeline

```{r}
tl1 = jsonlite::fromJSON('scrape/riot/raw/matchtimeline/160160.json')
tl2 = jsonlite::fromJSON('scrape/riot/raw/matchtimeline/160172.json')

tl1 %>% names
thing = unnest(tl1$frames)

```


missing timestamp key in each timeframe...

```{r}
tl10 = list.files( "scrape/riot/raw/matchtimeline/", full.names=TRUE) %>% 
  head() %>% 
  map_df(function(x) { 
    map(jsonlite::fromJSON(x), function(y) ifelse(is.null(y), y, y)) 
  })
```

```{r}
try_filter <- function(df) {
  tryCatch(
    df %>%
      filter(Sepal.Length == 4.6),
    error = function(e) data.frame())
}


tl10 = list.files( "scrape/riot/raw/matchtimeline/", full.names=TRUE) %>% 
  head() %>% 
  map_df(jsonlite::fromJSON, try_filter)
```

```{r}
files =list.files( "scrape/riot/raw/matchtimeline/", full.names=TRUE)

pages <- list()
for(file in files){
  pages[[length(pages)+1]] <- jsonlite::fromJSON(file)$frames
}

tlrbind <- rbind_pages(pages)

```


okayyy lets just use some csvs
```{r}
frames <- list.files("scrape/riot/raw/matchtimeline-frames/", full.names = TRUE) %>% 
  map_df(read_csv)

frames = frames %>% 
  mutate(
      isBlue = participantId < 6,
      team = ifelse(isBlue, 'B', 'R')
    )
```

how much gold at 15 minutes?

```{r}
golddif = frames %>% 
  group_by(game, timestamp, team) %>% 
  summarise(gold = sum(totalGold)) %>% 
  spread(team, gold) %>% 
  mutate(dif = R - B)


golddif %>% 
  filter(60000*5 < timestamp & timestamp < 60000*25) %>% 
  ggplot(aes(dif/(R + B))) +
  geom_histogram() +
  facet_wrap(~timestamp)
```

## chart gold difference and victory time



## line charts of all cs per minute


## chance of winning a losing game


## number of champs picked each patch


## time since champ was picked
 xin hasn't been picked in NA for since 2015


## how far behind the meta is NA


















